---
title: "CTSBS Age-Mixing"
author: "Roxanne Beauclair"
date: '`r format(Sys.Date(), "%d %b %Y")`'
output: html_document
---

```{r setup, include = FALSE}
# ===================
# Relative file paths
# ===================
wd <- "/Users/roxannebeauclair/Documents/Analytical Projects/PhD/CTSbS Age Mixing/Analysis"
cdata <- paste0(wd, "/Data/Cleaned")

concurdata <- paste0(cdata, "/ctsbs_concur_added_data.rda")
imputedata <- paste0(cdata, "/ctsbs_impute_data.rda")
imputedatapart <- paste0(cdata, "/ctsbs_impute_data_part.rda")
bootdata <- paste0(cdata, "/ctsbs_boot_rbind_data.rda")

fxn <- paste0(wd, "/Scripts/00-Functions.R")

# ====================
# Loading dependencies
# ====================
source(fxn)

# magrittr: for use of %>% operator
# tidyverse: for data management functions
# mice: for MI


InstallLoad("magrittr", "MASS", "tidyverse", 
            "mice","nlme", "lme4", "modelr",
            "mgcv", "gamm4", "broom", "splines", 
            "mediation", "forcats", "Gmisc", "htmlTable")

# =============
# Load datasets
# =============
load(imputedata)
load(imputedatapart)
load(concurdata)
load(bootdata)

# ====================
# Set specific global options
# ====================

# Set theme for plots
theme <- theme(axis.title.x = element_text(face = "bold", size = 10),
             axis.text.x  = element_text(angle = 0, face = "bold",
                                         colour = "black", size = 8),
             axis.title.y = element_text(face = "bold", size = 10),
             axis.text.y = element_text(angle = 0, 
                                        face = "bold", 
                                        colour = "black", 
                                        hjust = 0.5,
                                        size = 8),
             plot.title = element_text(lineheight = .8, face = "bold"),
             panel.grid.major = element_line(colour = 'grey82'),
             panel.grid.minor = element_line(colour = NA),
             panel.background = element_rect(fill = 'white'),
             strip.background = element_rect(fill = 'white'),
             strip.text = element_text(size = 8, face = "bold"),
             legend.title = element_text(colour = "black", size = 9, face = "bold"),
             legend.text = element_text(size = 8, face = "bold"),
             plot.margin = unit(c(1.5,1,1,1), "lines"))


# Initialize table counter
options(show.signif.stars = F)

```


```{r df_description, include = FALSE}
# How many participants
df1 <- df %>%
  distinct(id, .keep_all = TRUE)

# How many exclusions due to sexuality
df2 <- df %>%
  filter(sexorientation != "Both" | is.na(sexorientation)) %>%
  filter((sex == "Male" & sexorientation == "Women") |
           ((sex == "Female" & sexorientation == "Men")) |
              (is.na(sex)))

# Participants left
df3 <- df2 %>% distinct(id)

n_sexuality <- nrow(df1) - nrow(df3)

# How many exclusions due to race
df4 <- df2 %>%
  filter(race == "Black")

# Participants left
df5 <- df4 %>% distinct(id)

n_race <- nrow(df3) - nrow(df5)

# How many exclusions due to no parter reported
df6 <- df4 %>%
  filter(partner != 0) %>%
  droplevels()

# Participants left
df7 <- df6 %>% distinct(id)

n_nopart <- nrow(df5) - nrow(df7)

# How many participants left
parts_left <- nrow(df7)

# How many relationships left
rels_left <- nrow(df6)

# How many participants had more than 1 relationship
parts_many_partner <- partdfimp %>%
  filter(.imp == 0) %>%
  filter(relcount > 1) %>%
  nrow()


rm(df, df1, df2, df3, df4, df5, df6, df7)

imp <- max(as.integer(dfimp$.imp)) - 1


```

<br>

**Research questions:** 

1. Describe the age-mixing pattern in the CTSBS population. Do age-mixing patterns differ between:

* HIV positive men and women
* HIV negative men and women
* HIV positive and HIV negative men
* HIV positive and HIV negative women 

2. At the individual-level are large ranges in partner ages (bridgewidths) associated with HIV status of a participant?

Before conducting imputations, I excluded participants who said their sexual preferences were for "both" genders or the same gender (n = `r n_sexuality`). I further excluded people who did not identify as black(n = `r n_race`) and people who did not report partners in the previous year (n = `r n_nopart`).  This left `r rels_left` relationships reported by `r parts_left` participants. Of the `r parts_left` participants, `r parts_many_partner` reported more than one relationship in the previous year. I imputed `r imp` datasets using the random forest method for continuous and nominal categorical variables and the "polr" method for our ordinal variables. 

<br>


```{r hiv_prev, echo = FALSE, warning = FALSE}

set.seed(209)
n <- sample(1:imp, 1)

hivprev <- partdfimp %>%
  filter(.imp == n) %>%
  mutate(agegroup = cut(age,
                        breaks = c(0, 24, 29, 34, 
                                   39, 44, 49, 54, 59,
                                   70),
                        labels = c("15-24", "25-29", 
                                   "30-34", "35-39", "40-44", 
                                   "45-49", "50-54", "55-59", 
                                   "60+"))) %>%
  group_by(sex, agegroup, hiv) %>%
  summarise(n = n()) %>%
  mutate(total = sum(n),
         prop = n / total) %>%
  ungroup() %>%
  group_by(sex, agegroup, hiv, n, total) %>%          # The binom.test() function is not vectorized,
  mutate(ll = binom.test(n, total)$conf.int[1],       # and thus, we need to make sure each row is   
         ul = binom.test(n, total)$conf.int[2])       # treated as an individual data frame

hivprevplot <- hivprev %>%
  filter(hiv == "Positive") %>%
  ggplot(aes(x = agegroup, y = prop, fill = sex)) +
  geom_bar(stat = "identity",
           position = position_dodge()) +
  geom_errorbar(aes(ymax = ul, ymin = ll),
                position = position_dodge(0.9),
                width = 0.10) +
  xlab("Age group") +
  ylab("Proportion") +
  scale_fill_hue(name = "Gender") +
  theme

hivprevplot
  

```


###### **Figure 1. HIV prevalence by sex and age in randomly selected imputed dataset**


<br>

```{r multiple partners_setup, include = FALSE, warning = FALSE}
dfmpm <- partdfimp %>% 
  filter(.imp == n & 
           sex == "Male") %>%
  mutate(mp = as.factor(ifelse(relcount > 1, "Multiple", "One"))) 

dfmpw <- partdfimp %>%
  filter(.imp == n & 
           sex == "Female") %>%
  mutate(mp = as.factor(ifelse(relcount > 1, "Multiple", "One"))) 

agem <- GetT1Stat(dfmpm$agegroup, dfmpm$mp)
agew <- GetT1Stat(dfmpw$agegroup, dfmpw$mp)

hivm <- GetT1Stat(dfmpm$hiv, dfmpm$mp)
hivw <- GetT1Stat(dfmpw$hiv, dfmpw$mp)


tab1 <- list()

tab1[["Age"]] <- cbind(agew, agem)
tab1[["HIV status"]] <- cbind(hivm, hivw)
```

```{r multiple_partners_table, include = FALSE, warning = FALSE}
mergeDesc(tab1) %>%
  htmlTable(caption = "<b>Appendix Table 1. Proportion of participants reporting more than 1 partner<b/>",
            tfoot = "Categories are reported in percentages, n (%).",
            cgroup = c("Women", "Men"), 
            n.cgroup = c(2, 2), 
            ctable = TRUE,
            padding.rgroup = "&nbsp; &nbsp; &nbsp;")

```


<br>

```{r slope_int_setup, include = FALSE, warning = FALSE}
# Unnest tidy summary for data on slope and intercept
# of all the models
modslopeint <- ampdf %>%
  unnest(modelsum, .drop = TRUE)

modslopeint

# Create df where the terms are in wide format according
# to subgroup, so that we can calculate differences
slopeintdif <- modslopeint %>%
  select(-std.error, -statistic) %>%
  unite(subpop, sex, hiv) %>%
  spread(subpop, estimate) 

slopeintdif

# Calculate differences in slopes for:
# 1. Males vs. Females in neg population
# 2. Males vs. Females in pos population
# 3. Pos vs Neg in male population
# 4. Pos vs Neg in female population

difslopesum <- slopeintdif %>%
  filter(term == "age0") %>%
  mutate(gendifneg = Female_Negative - Male_Negative, # Ha: Female slopes larger than males
         gendifpos = Female_Positive - Male_Positive, # Ha; Female slopes larger than males
         hivdifmale = Male_Negative - Male_Positive, # Ha: Negative slopes larger than pos
         hivdiffemale = Female_Negative - Female_Positive) # Ha: Neg slopes larger than pos

difslopesum

# Calculate differences in intercepts for:
# 1. Males vs. Females in neg population
# 2. Males vs. Females in pos population
# 3. Pos vs Neg in male population
# 4. Pos vs Neg in female population

difintsum <- slopeintdif %>%
  filter(term == "(Intercept)") %>%
  mutate(gendifneg = Female_Negative - Male_Negative, # Ha: Female intercepts larger than males
         gendifpos = Female_Positive - Male_Positive, # Ha; Female intercepts larger than males
         hivdifmale = Male_Positive - Male_Negative, # Ha: Pos intercepts larger than neg
         hivdiffemale = Female_Positive - Female_Negative) # Ha: Pos intercepts larger than neg

difintsum

# Now take all of the estimates and calculate CI's using percentile method
alpha = 0.05

slopeintci <- modslopeint %>%
  group_by(term, sex, hiv) %>%
  summarise(mean = mean(estimate),
            lwr = quantile(estimate, alpha / 2),
            upr = quantile(estimate, 1- alpha / 2))

slopeintci

slopedifci <- difslopesum %>%
  summarise(meangendifneg = mean(gendifneg),
            meangendifpos = mean(gendifpos),
            meanhivdifmale = mean(hivdifmale),
            meanhivdiffemale = mean(hivdiffemale),
            lwrgendifneg = quantile(gendifneg, alpha / 2),
            lwrgendifpos = quantile(gendifpos, alpha / 2),
            lwrhivdifmale = quantile(hivdifmale, alpha / 2),
            lwrhivdiffemale = quantile(hivdiffemale, alpha / 2),
            uprgendifneg = quantile(gendifneg, 1 - alpha / 2),
            uprgendifpos = quantile(gendifpos, 1 - alpha / 2),
            uprhivdifmale = quantile(hivdifmale, 1 - alpha / 2),
            uprhivdiffemale = quantile(hivdiffemale, 1 - alpha / 2)) %>%
  mutate_all(funs(round(., 2)))

intdifci <- difintsum %>%
  summarise(meangendifneg = mean(gendifneg),
            meangendifpos = mean(gendifpos),
            meanhivdifmale = mean(hivdifmale),
            meanhivdiffemale = mean(hivdiffemale),
            lwrgendifneg = quantile(gendifneg, alpha / 2),
            lwrgendifpos = quantile(gendifpos, alpha / 2),
            lwrhivdifmale = quantile(hivdifmale, alpha / 2),
            lwrhivdiffemale = quantile(hivdiffemale, alpha / 2),
            uprgendifneg = quantile(gendifneg, 1 - alpha / 2),
            uprgendifpos = quantile(gendifpos, 1 - alpha / 2),
            uprhivdifmale = quantile(hivdifmale, 1 - alpha / 2),
            uprhivdiffemale = quantile(hivdiffemale, 1 - alpha / 2)) %>%
  mutate_all(funs(round(., 2)))

```

```{r wvar_setup, include = FALSE, warning = FALSE}

# Unnest tidy summary for data on within individual variance
modwvar <- ampdf %>%
  unnest(wvar, .drop = TRUE) 

modwvar

wvardif <- modwvar %>%
  select(-lwrwsd, -uprwsd) %>%
  unite(subpop, sex, hiv) %>%
  spread(subpop, wsd) 

wvardif

# Calculate differences in within-subject sd for:
# 1. Males vs. Females in neg population
# 2. Males vs. Females in pos population
# 3. Pos vs Neg in male population
# 4. Pos vs Neg in female population

difwvarsum <- wvardif %>%
  mutate(gendifneg = Male_Negative - Female_Negative, # Ha: Male wvar larger than females
         gendifpos = Female_Positive - Male_Positive, # Ha: Female wvar larger than males
         hivdifmale = Male_Positive - Male_Negative, # Ha: Pos wvar larger than neg
         hivdiffemale = Female_Positive - Female_Negative) # Ha: Pos wvar larger than neg
         
difwvarsum

# Now take all of the wvars and calculate CI's using percentile method
alpha = 0.05

wsdci <- modwvar %>%
  group_by(sex, hiv) %>%
  summarise(mean = mean(wsd),
            lwr = quantile(wsd, alpha / 2),
            upr = quantile(wsd, 1 - alpha / 2))

wsdci

wvardifci <- difwvarsum %>%
  summarise(meangendifneg = mean(gendifneg),
            meanhivdifmale = mean(hivdifmale),
            meangendifpos = mean(gendifpos),
            meanhivdiffemale = mean(hivdiffemale),
            lwrgendifneg = quantile(gendifneg, alpha / 2),
            lwrhivdifmale = quantile(hivdifmale, alpha / 2),
            lwrgendifpos = quantile(gendifpos, alpha / 2),
            lwrhivdiffemale = quantile(hivdiffemale, alpha / 2),
            uprgendifneg = quantile(gendifneg, 1 - alpha / 2),
            uprhivdifmale = quantile(hivdifmale, 1 - alpha / 2),
            uprgendifpos = quantile(gendifpos, 1 - alpha / 2),
            uprhivdiffemale = quantile(hivdiffemale, 1 - alpha / 2)) %>%
  mutate_all(funs(round(., 2)))


```

```{r bvar_setup, include = FALSE, warning = FALSE}
# Range of partner ages for HIV positive men in CC
pagerange <- dfimp %>%
  filter(.imp == 0,
         sex == "Male",
         hiv == "Positive") 

nhivmen <- nrow(pagerange)
pagerangemin <- summary(pagerange$agep)[[1]]
pagerangemax <- summary(pagerange$agep)[[6]]
  

# Unnest tidy summary for data on between individual variance
modbvar <- ampdf %>%
  unnest(bvar, .drop = TRUE)

modbvar

bvardif <- modbvar %>%
  select(-lwrbsd, -uprbsd) %>%
  unite(subpop, sex, hiv) %>%
  spread(subpop, bsd) 

bvardif

# Calculate differences in between-subject sd for:
# 1. Males vs. Females in neg population
# 2. Males vs. Females in pos population
# 3. Pos vs Neg in male population
# 4. Pos vs Neg in female population

difbvarsum <- bvardif %>%
  mutate(gendifneg = Male_Negative - Female_Negative, # Ha: Male bvar larger than females
         gendifpos = Male_Positive - Female_Positive, # Ha; Male bvar larger than females
         hivdifmale = Male_Negative - Male_Positive, # Ha: Neg bvar larger than pos
         hivdiffemale = Female_Negative - Female_Positive) # Ha: Neg bvar larger than pos

difbvarsum

# Now take all of the bvars and calculate CI's using percentile method
alpha = 0.05

bsdci <- modbvar %>%
  group_by(sex, hiv) %>%
  summarise(mean = mean(bsd),
            lwr = quantile(bsd, alpha / 2),
            upr = quantile(bsd, 1- alpha / 2))

bsdci

bvardifci <- difbvarsum %>%
  summarise(meangendifneg = mean(gendifneg),
            meangendifpos = mean(gendifpos),
            meanhivdifmale = mean(hivdifmale),
            meanhivdiffemale = mean(hivdiffemale),
            lwrgendifneg = quantile(gendifneg, alpha / 2),
            lwrgendifpos = quantile(gendifpos, alpha / 2),
            lwrhivdifmale = quantile(hivdifmale, alpha / 2),
            lwrhivdiffemale = quantile(hivdiffemale, alpha / 2),
            uprgendifneg = quantile(gendifneg, 1 - alpha / 2),
            uprgendifpos = quantile(gendifpos, 1 - alpha / 2),
            uprhivdifmale = quantile(hivdifmale, 1 - alpha / 2),
            uprhivdiffemale = quantile(hivdiffemale, 1 - alpha / 2)) %>%
  mutate_all(funs(round(., 2)))
```


```{r amp_model_slope_plot, echo = FALSE, warning = FALSE, fig.height = 8}

# Plot all of the beta's for age mixing pattern in 
# each of the datasets (by imputation and gender)
means <- slopeintci %>%
  filter(term == "age0") 

label <- c(
   paste0("Mean: ", round(means$mean[1], 2), " (", round(means$lwr[1], 2), "-", round(means$upr[1], 2), ")"),
   paste0("Mean: ", round(means$mean[3], 2), " (", round(means$lwr[3], 2), "-", round(means$upr[3], 2), ")"),
   paste0("Mean: ", round(means$mean[2], 2), " (", round(means$lwr[2], 2), "-", round(means$upr[2], 2), ")"),
   paste0("Mean: ", round(means$mean[4], 2), " (", round(means$lwr[4], 2), "-", "0.80)") 
 ) # The last one was manually entered because the formatting leaves off the zero.

slopeplot <- modslopeint %>%
  filter(term == "age0") %>%
  ggplot(aes(x = estimate)) +
  geom_density(alpha = 0.2, fill = "blue") +
  geom_vline(aes(xintercept = mean), 
             data = means,
             linetype = "dashed") +
  geom_vline(aes(xintercept = lwr), 
             data = means,
             linetype = "dashed") +
  geom_vline(aes(xintercept = upr), 
             data = means,
             linetype = "dashed") +
  facet_grid(hiv ~ sex) +
  xlab("Beta-Coefficients") +
  annotate("text", x = 0.0, y = 7, 
           label = label,
           size = 3.0) +
  theme

slopeplot
```

###### **Figure 2. Distribution of age-mixing model slopes for 100 imputed datasets, each bootstraped 2000 times.**

<br>



```{r amp_model_intercept_plot, echo = FALSE, warning = FALSE, fig.height = 8}

# Plot all of the intercepts for age mixing pattern in 
# each of the  datasets (by imputation and gender)
means <- slopeintci %>%
  filter(term == "(Intercept)")

label <- c(
   paste0("Mean: ", round(means$mean[1], 2), " (", round(means$lwr[1], 2), "-", round(means$upr[1], 2), ")"),
   paste0("Mean: ", round(means$mean[3], 2), " (", round(means$lwr[3], 2), "-", round(means$upr[3], 2), ")"),
   paste0("Mean: ", "25.10", " (", round(means$lwr[2], 2), "-", round(means$upr[2], 2), ")"),
   paste0("Mean: ", "23.00", " (", round(means$lwr[4], 2), "-", round(means$upr[4], 2), ")")
 )

interplot <- modslopeint %>%
  filter(term == "(Intercept)") %>%
  ggplot(aes(x = estimate)) +
  geom_density(alpha = 0.2, fill = "blue") +
  geom_vline(aes(xintercept = mean), 
             data = means,
             linetype = "dashed") +
  geom_vline(aes(xintercept = lwr), 
             data = means,
             linetype = "dashed") +
  geom_vline(aes(xintercept = upr), 
             data = means,
             linetype = "dashed") +
  facet_grid(hiv ~ sex) +
  xlab("Partner age for 15 year olds") +
  annotate("text", x = 40, y = 0.30, 
           label = label,
           size = 3.0) +
  theme

interplot
```

###### **Figure 3. Distribution of age-mixing model intercepts for 1000 imputed datasets, each bootstraped 2000 times.**

<br>


```{r amp_model_bvar_plot, echo = FALSE, warning = FALSE, fig.height = 8}

label <- c(
   paste0("Mean: ", round(bsdci$mean[1], 2), " (", round(bsdci$lwr[1], 2), "-", round(bsdci$upr[1], 2), ")"),
   paste0("Mean: ", round(bsdci$mean[3], 2), " (", round(bsdci$lwr[3], 2), "-", round(bsdci$upr[3], 2), ")"),
   paste0("Mean: ", round(bsdci$mean[2], 2), " (", round(bsdci$lwr[2], 2), "-", round(bsdci$upr[2], 2), ")"),
   paste0("Mean: ", round(bsdci$mean[4], 2), " (", round(bsdci$lwr[4], 2), "-", round(bsdci$upr[4], 2), ")") 
 ) 

# Plot each of the between subject variances for age mixing pattern
# in each of the datasets (by imputation and gender)
bvarplot <- modbvar %>%
  ggplot(aes(x = bsd)) +
  geom_density(alpha = 0.2, fill = "blue") +
  geom_vline(aes(xintercept = mean), 
             data = bsdci,
             linetype = "dashed") +
  geom_vline(aes(xintercept = lwr), 
             data = bsdci,
             linetype = "dashed") +
  geom_vline(aes(xintercept = upr), 
             data = bsdci,
             linetype = "dashed") +
  facet_grid(hiv ~ sex) +
  xlab("Between-subject Standard Deviation") +
  annotate("text", x = 5, y = 0.4, 
           label = label,
           size = 3.0) +
  theme

bvarplot
```


###### **Figure 4. Distribution of age-mixing between-subject standard deviations (BSSD) for 100 imputed datasets, each bootstraped 2000 times.** 

The HIV positive black men had only contributed `r nhivmen` complete cases of relationships. Among the complete cases in this sub-population the minimum age was `r pagerangemin` and the maximum partner ages was `r pagerangemax`. Because there were so few complete relationships, the extreme values were probably over-sampled in some of the bootstrap replications, which is why we see more of a bimodal distribution. 

<br>

```{r amp_model_wvar_plot, echo = FALSE, warning = FALSE, fig.height = 8}

label <- c(
   paste0("Mean: ", round(wsdci$mean[1], 2), " (", round(wsdci$lwr[1], 2), "-", round(wsdci$upr[1], 2), ")"),
   paste0("Mean: ", round(wsdci$mean[3], 2), " (", round(wsdci$lwr[3], 2), "-", "6.40)"),
   paste0("Mean: ", round(wsdci$mean[2], 2), " (", round(wsdci$lwr[2], 2), "-", round(wsdci$upr[2], 2), ")"),
   paste0("Mean: ", round(wsdci$mean[4], 2), " (", round(wsdci$lwr[4], 2), "-", round(wsdci$upr[4], 2), ")") 
 ) 

# Plot each of the residual variances for age mixing pattern
# in each of the datasets (by imputation and gender)
wvarplot <- modwvar %>%
  ggplot(aes(x = wsd)) +
  geom_density(alpha = 0.2, fill = "blue") +
  geom_vline(aes(xintercept = mean), 
             data = wsdci,
             linetype = "dashed") +
  geom_vline(aes(xintercept = lwr), 
             data = wsdci,
             linetype = "dashed") +
  geom_vline(aes(xintercept = upr), 
             data = wsdci,
             linetype = "dashed") +
  facet_grid(hiv ~ sex) +
  xlab("Within-subject Standard Deviation") +
  annotate("text", x = 11, y = 0.5, 
           label = label,
           size = 3.0) +
  theme

wvarplot
```

###### **Figure 5. Distribution of age-mixing within-subject standard deviations (WSSD) for 100 imputed datasets, each bootstraped 2000 times.**


<br>



```{r table 1 setup, include = FALSE}

# Matrix for  model results
mx <- matrix(ncol = 4, nrow = 4)
rownames(mx) <- c("HNM vs. HNW", "HPM vs. HPW", "HPM vs. HNM", "HPW vs. HNW")
colnames(mx) <- c("B-coefficient", 
                  "Intercept", 
                  "BSSD", 
                  "WSSD")


# slopedifci <- format(slopedifci, digits = 2)
# intdifci <- format(intdifci, digits = 2)
# bvardifci <- format(bvardifci, digits = 2)
# wvardifci <- format(wvardifci, digits = 2)

mx[1, 1] <- paste0(slopedifci$meangendifneg, " (", slopedifci$lwrgendifneg, " — ", slopedifci$uprgendifneg, ")")
mx[2, 1] <- paste0(slopedifci$meangendifpos, " (", slopedifci$lwrgendifpos, " — ", slopedifci$uprgendifpos, ")")
mx[3, 1] <- paste0(slopedifci$meanhivdifmale, " (", slopedifci$lwrhivdifmale, " — ", slopedifci$uprhivdifmale, ")")
mx[4, 1] <- paste0(slopedifci$meanhivdiffemale, " (", slopedifci$lwrhivdiffemale, " — ", slopedifci$uprhivdiffemale, ")")

mx[1, 2] <- paste0(intdifci$meangendifneg, " (", intdifci$lwrgendifneg, " — ", intdifci$uprgendifneg, ")")
mx[2, 2] <- paste0(intdifci$meangendifpos, " (", intdifci$lwrgendifpos, " — ", intdifci$uprgendifpos, ")")
mx[3, 2] <- paste0(intdifci$meanhivdifmale, " (", intdifci$lwrhivdifmale, " — ", intdifci$uprhivdifmale, ")")
mx[4, 2] <- paste0(intdifci$meanhivdiffemale, " (", intdifci$lwrhivdiffemale, " — ", intdifci$uprhivdiffemale, ")")

mx[1, 3] <- paste0(bvardifci$meangendifneg, " (", bvardifci$lwrgendifneg, " — ", bvardifci$uprgendifneg, ")")
mx[2, 3] <- paste0(bvardifci$meangendifpos, " (", bvardifci$lwrgendifpos, " — ", bvardifci$uprgendifpos, ")")
mx[3, 3] <- paste0(bvardifci$meanhivdifmale, " (", bvardifci$lwrhivdifmale, " — ", bvardifci$uprhivdifmale, ")")
mx[4, 3] <- paste0(bvardifci$meanhivdiffemale, " (", bvardifci$lwrhivdiffemale, " — ", bvardifci$uprhivdiffemale, ")")

mx[1, 4] <- paste0(wvardifci$meangendifneg, " (", wvardifci$lwrgendifneg, " — ", wvardifci$uprgendifneg, ")")
mx[2, 4] <- paste0(wvardifci$meangendifpos, " (", wvardifci$lwrgendifpos, " — ", wvardifci$uprgendifpos, ")")
mx[3, 4] <- paste0(wvardifci$meanhivdifmale, " (", wvardifci$lwrhivdifmale, " — ", wvardifci$uprhivdifmale, ")")
mx[4, 4] <- paste0(wvardifci$meanhivdiffemale, " (", wvardifci$lwrhivdiffemale, " — ", wvardifci$uprhivdiffemale, ")")

```


<br>


```{r table 1, echo = FALSE, fig.width = 10}

# Male models table
mx %>%
  htmlTable(caption = "<b>Table 1. Differences between age-mixing pattern model features.</b>",
            tfoot = txtMergeLines("HNM, HIV Negative Men", 
                                 "HNW, HIV Negative Women",
                                 "HPM, HIV Positive Men",
                                 "HPW, HIV Positive Women",
                                 "BSSD, Between-subject Standard Deviation",
                                 "WSSD, Within-subject Standard Deviation",
                                 "These differences are calculated from 200,000 datasets"),
            rowlabel = "Comparisons",
            ctable = TRUE)

```



```{r age_hiv_fig, include = FALSE, warning = FALSE, fig.height = 8}
# Create dataframe that summarizes the proportion of relationships
# in different partner age groups for people who are HIV
# positive
hivbyage <- dfimp %>%
  filter(.imp == n & hiv == "Positive") %>%
  group_by(sex, agepgroup) %>%
  summarise(n = n()) %>%
  mutate(prop = round((n / sum(n)) * 100, 2))

# barplot of fraction of relationships in different partner age groups  
hivageplot <- hivbyage %>%
  ggplot(aes(x = agepgroup, y = prop, fill = sex)) +
  geom_bar(stat = "identity",
           position = position_dodge()) +
  xlab("Age group of partner") +
  ylab("Proportion of relationships") +
  scale_fill_brewer(palette = "Dark2") +
  theme

hivageplot
  
```


<br>

```{r bw_hiv_setup, include = FALSE, warning = FALSE}
# Exclude complete cases dataframe
# Keep only participants with more than one relationship in the past year
impsex <- partdfimp %>% 
  filter(.imp != 0) %>%
  group_by(.imp, sex) 

# Summarize the median and IQR of bW by sex and dataset
# Among those with more than 1 partner
bwbyimpsex <- impsex %>%
  filter(relcount > 1) %>%
  summarise(n = n(),
            Median = median(bridgewidth),
            Mean = mean(bridgewidth),
            sd = sd(bridgewidth),
            lwr = summary(bridgewidth)[[2]],
            upr = summary(bridgewidth)[[5]])

# Nest all the datasets by sex and imputation
impsexbw <- impsex %>% 
  filter(relcount > 1) %>%
  nest()

# Does HIV predict bridgewidths (neg bin models)?
# Does HIV predict whether a participant had a concurrent rel in past year (logistic models)?

tidysum <- impsexbw %>% # A model will be applied to all imputations and sex
  mutate(modelbw = map(data, bwmodel),
         modelsumbw = map(modelbw, tidygam), # Create tidy summary of each model and store as modelsum var in nested df
         predsbwage = map(modelbw, gampredsage)) # Create predictions across dif vals of age (our spline var))

# Unnest the tidy summary, to see the tidy model estimates for each model
bwmodcoef <- tidysum %>%
  unnest(modelsumbw, .drop = TRUE) 

# Unnest the tidy summary, to see the tidy model predictions for values of age
# for each model
bwmodpredage <- tidysum %>%
  unnest(predsbwage, .drop = TRUE)

```



```{r pool_bw_coef, include = FALSE, warning = FALSE}

# Now we want to produce a pooled beta for HIV according to 
# Rubin's rules. To do this we use mice functions


part <- partdfimp %>% # Take original participant-level imputed df
   mutate(bridgewidth = ifelse(bridgewidth == -Inf | bridgewidth == Inf, 
                               NA, bridgewidth)) %>% # Change Inf, -Inf from CC data to NA
   filter(relcount > 1) %>% # Only participants who had more than one rel
   as.mids() # Create mids object
 
bwmodpoolm <- part %>%
   with(gam(bridgewidth ~ hiv + s(age),
         family = nb(),
         subset = (sex == "Male")) 
        ) %>%
   pool() %>% # Pool coefficients according to Rubin's Rules
   summary() %>%
   exp() %>%
   round(2) 
 
bwmodpoolw <- part %>%
   with(
     gam(bridgewidth ~ hiv + s(age),
         family = nb(),
         subset = (sex == "Female"))
     ) %>%
   pool() %>% # Pool according to Rubin's Rules
   summary() %>%
   exp() %>%
   round(2) 
 
 menEBWR <- bwmodpoolm[2, 1] # Extract HIV EBWR 
 menEBWRlwr <- bwmodpoolm[2, 6] # Extract HIV lower CI limit
 menEBWRupr <- bwmodpoolm[2, 7] # Extract HIV upper CI limit
 womenEBWR <- bwmodpoolw[2, 1]
 womenEBWRlwr <- bwmodpoolw[2, 6]
 womenEBWRupr <- bwmodpoolw[2, 7]
 
```


```{r bw_dist_figs_setup, include = FALSE, warning = FALSE}
bwdf <- partdfimp %>% 
  filter(.imp != 0 &
           relcount > 1) 

```

<br>

```{r bw_hiv_density_fig, echo = FALSE, warning = FALSE}

# Check spread of bridgwidths for each grouped dataset
bwhivfig <- bwdf %>%
  ggplot(aes(x = bridgewidth, group = .imp)) +
  geom_density(adjust = 2) +
  facet_grid(hiv ~ sex) +
  xlab("Bridge Width") +
  ylab("Density") +
  theme

bwhivfig
```

###### **Figure 6. Distribution of bridge widths among those reporting more than one partner for each imputed dataset, by sex and HIV status.**

<br>


```{r bw_hiv_fig, echo = FALSE, warning = FALSE}

yticks <- c(0.5, 1.0, 2.0, 4.0)
xticks <- seq(from = 0, to = 100, by = 10)

 label <- c(
   paste0("Pooled EBWR: ", menEBWR, "(", menEBWRlwr, "-", menEBWRupr, ")"),
   paste0("Pooled EBWR: ", womenEBWR, "(", womenEBWRlwr, "-", womenEBWRupr, ")")
 )

# Plot all the b's for each imputed dataset by sex
# Annotate with the pooled coefficient from above
bwhivfig <- bwmodcoef %>%
  filter(term == "hivPositive") %>%
  mutate(.imp = as.numeric(.imp) - 1) %>%
  ggplot(aes(x = .imp, ratio)) +
   geom_hline(yintercept = 1, 
             color = "blue") +
  geom_point() +
  geom_pointrange(aes(ymax = rupr,
                      ymin = rlwr)) +
  facet_grid(sex ~ .) +
  xlab("Imputation") +
  ylab("Expected Bridge Width Ratio") +
  scale_x_continuous(breaks = xticks) +
  scale_y_log10(breaks = yticks) +
  annotate("text", x = 80, y = 0.35, 
           label = label,
           size = 3.5) +
  theme

bwhivfig
```


###### **Figure 7. Model coefficients for relationship between HIV and bridgewidth.**

<br>


```{r bw_age_fig, echo = FALSE, warning = FALSE}

# Plot expected BW's for different values of age (or spline variable)
# Spaghetti plot to show each line for dataset by gender
bwagefig <- bwmodpredage %>%
  ggplot(aes(x = age, y = pred, group = .imp)) +
  geom_line(aes(alpha = 0.05)) +
  facet_grid(. ~ sex) +
  xlab("Age") +
  ylab("Expected Bridge Width") +
  guides(alpha = "none") +
  theme

bwagefig

```

###### **Figure 8. Expected bridge widths for different values of age (smooth term), by gender.**

<br>

```{r page_at_540, include = FALSE, warning = FALSE}
# formula for calculating average partner age
# page = B-Age * (Age) + Intercept
# 40 years minus 15 years (because we've centred on 15)

# HNM
pagehnm40 <- round((slopeintci$mean[7] * 25) + slopeintci$mean[3])

# HNW
pagehnw40 <- round((slopeintci$mean[5] * 25) + slopeintci$mean[1])

# HPW
pagehpw40 <- round((slopeintci$mean[6] * 25) + slopeintci$mean[2])

# HPM
pagehpm40 <- round((slopeintci$mean[8] * 25) + slopeintci$mean[4])

# Partner age at 25 (25years - 15years, because of centering)

# HNM
pagehnm25 <- round((slopeintci$mean[7] * 10) + slopeintci$mean[3])

# HNW
pagehnw25 <- round((slopeintci$mean[5] * 10) + slopeintci$mean[1])

# HPW
pagehpw25 <- round((slopeintci$mean[6] * 10) + slopeintci$mean[2])

# HPM
pagehpm25 <- round((slopeintci$mean[8] * 10) + slopeintci$mean[4])


```


### **KEY RESULTS TO DISCUSS**

1. Not much difference between the slopes in each sub-population: Average partner age increases with each year increase in participant age between: `r round(slopeintci$lwr[8], 2)` and `r round(slopeintci$upr[5], 2)`. HPW have steep slopes than HNM...meaning the age gaps are increasing more for women as they get older. 

2. When HIV negative men and women are 15 years old, the average difference between the population average partner age is approximately 5 years, with men having female partners who are `r round(slopeintci$mean[3])` years old on average and women `r round(slopeintci$mean[1])` years old on average. I think it is important to note here that young men also have older partners, and in Figure 1 we see that `r round(hivprev$prop[20] * 100, 1)`% of 15-24 year old women are HIV positive, compared to roughly `r round(hivprev$prop[2] * 100, 1)`% of men. Also the HIV positive 15 year olds seem to choose even older partners (mean: `r round(slopeintci$mean[4])`) although the distribution is more widespread.

3. HIV positive women have larger wsd's AND bsd's than HIV negative women. Women with HIV are also expected to have nearly 3 times larger bridgewidths than HIV negative women. Are women actually driving HIV transmission?

4. Expected bridgewidths probably increase with age in both men and women, although in women there is a slight hint that younger and older women might have higher BW's than middle-aged women.

### **RESULTS**

We randomly selected one of the 100 imputed data sets from which to calculate the HIV prevalence in our Cape Town study population (Figure 1). In most age groups, women had a higher HIV prevalence than men. For women aged 15-24, their HIV prevalence was nearly 3.5 times that of the men in that same age group (`r round(hivprev$prop[20] * 100, 1)`% in women vs. `r round(hivprev$prop[2] * 100, 1)`% in men). This disparity was just as striking in 25-29-year-olds, with `r round(hivprev$prop[22] * 100, 1)`% of women infected and only `r round(hivprev$prop[4] * 100, 1)`% of men infected. HIV prevalence peaked in women 30-34 years old (`r round(hivprev$prop[24] * 100, 1)`%) and in men who were 40-44 (`r round(hivprev$prop[10] * 100, 1)`%).

Figure 2 shows the distribution of model β-coefficients, which represents how fast the partner ages grow as participants' ages increased. For all subpopulations the average partner ages increased with each year increase in participant age. HPM had the smallest average model slope (β: `r round(slopeintci$mean[8], 2)`; 95% CI: `r round(slopeintci$lwr[8], 2)` - `r round(slopeintci$upr[8], 2)`), while HNW had the largest (β: `r round(slopeintci$mean[5], 2)`; 95% CI: `r round(slopeintci$lwr[5], 2)` - `r round(slopeintci$upr[5], 2)`) (Figure 2). Most of the distributions seem to overlap to a great extent and in Table 1, we see there were not large differences in β-coefficients between the groups, with all differences overlapping with zero. Although, there is some evidence that HNW have steeper slopes than HNM (Diff: `r slopedifci$meangendifneg`; 95% CI: `r slopedifci$lwrgendifneg` - `r slopedifci$uprgendifneg`). Also in Table 1 we see that for the HNM and HNW the model intercept difference was approximately `r round(intdifci$meangendifneg)` years (95% CI: `r intdifci$lwrgendifneg` - `r intdifci$uprgendifneg`), with 15-year-old men and women in those groups having partners who were `r round(slopeintci$mean[3])` (95% CI: `r round(slopeintci$lwr[3])` - `r round(slopeintci$upr[3])`) and `r round(slopeintci$mean[1])`-years-old (95% CI: `r round(slopeintci$lwr[1])` - `r round(slopeintci$upr[1])`) on average, respectively (Figure 3). If we take the mean model slopes and intercepts for each subpopulation the average partner age at 25 years old is predicted to be `r pagehnw25` years for HNW, `r pagehnm25` years for HNM, `r pagehpw25` years for HPW, and `r pagehpm25` years for HPM. The predicted partner ages for 40 year olds is: `r pagehnw40` years for HNW, `r pagehnm40` years for HNM, `r pagehpw40` years for HPW, and `r pagehpm40` years for HPM.

HNM had the largest BSSD (BSSD: `r round(bsdci$mean[3], 2)`; 95% CI: `r round(bsdci$lwr[3], 2)` - `r round(bsdci$upr[3], 2)`) while HPW had the lowest (BSSD: `r round(bsdci$mean[2], 2)`; 95% CI: `r round(bsdci$lwr[2], 2)` - `r round(bsdci$upr[2], 2)`) (Figure 4). There appears to be a wide and bimodal distribution of BSSD's in HPM. In the complete case data there were only `r nhivmen` relationships in this subpopulation, with the minimum and maximum partner ages being `r pagerangemin` and `r pagerangemax`, respectively. We believe those extreme values were oversampled in the bootstrap replicates because of the small sample size, thus resulting in clusters of results with both small and large BSSDs. Therefore, we do not encourage readers to over-interpret the BSSDs for HPM in Figure 4. Table 1 shows that there was a relatively large and significant difference between the BSSD in HPW and HNW (Diff: `r bvardifci$meanhivdiffemale`; 95% CI: `r bvardifci$lwrhivdiffemale` - `r bvardifci$uprhivdiffemale`). 

Figure 5 shows that the WSSD was the largest for HPW (WSSD: `r round(wsdci$mean[2], 2)`; 95% CI: `r round(wsdci$lwr[2], 2)` - `r round(wsdci$upr[2], 2)`) and the smallest for HNW (WSSD: `r round(wsdci$mean[1], 2)`; 95% CI: `r round(wsdci$lwr[1], 2)` - `r round(wsdci$upr[1], 2)`), with the difference between the two groups being `r round(wvardifci$meanhivdiffemale, 2)` (95% CI: `r round(wvardifci$lwrhivdiffemale, 2)` - `r round(wvardifci$uprhivdiffemale, 2)`) (Table 1). For the other group comparisons, the WSSDs appear to be similar and their distributions have a large degree of overlap.

In the complete study population `r parts_many_partner` participants reported having more than one relationship in the previous year (`r round(parts_many_partner / parts_left * 100, 2)`%). Figure 6 shows the distribution of bridge widths — range in partner ages — by subpopulation. In all subpopulations the distributions were right-skewed, with most of the density in all imputations being less than 20 years. In both HIV positive groups, there appears to be fatter tails, implying that those with HIV may have larger bridge widths, although there is more uncertainty in the imputations of HPM. The results of our individual-level negative-binomial models are presented in Figures 7 and 8. Across all imputations, having an HIV-positive diagnosis increased the expected bridge width of women by almost `r round(womenEBWR)` times that of those who were HIV-negative (95% CI: `r womenEBWRlwr` - `r womenEBWRupr`). Among men there also seems to be an increased expectation of larger bridge widths in HIV positive participants compared to HIV negative participants, although when all of the estimates were pooled for the imputed data sets, the evidence did not appear to be as convincing as the evidence for women (EBWR: `r menEBWR`; 95% CI: `r menEBWRlwr` - `r menEBWRupr`). 

Finally, in both men and women there appears to be a relationship between increasing participant age and larger bridge widths, although the uncertainty in the imputations is reflected by there being large variation in expected bridge widths at older ages. For men the increase in the expected partner age ranges were not as large as for women. For women, in most of the imputed data sets, the relationship between age and expected bridge widths is non-linear, with the youngest and oldest participants having larger expected bridge widths, and those between 25 and 45 years old having smaller bridge widths. 



```{r close, include = FALSE, warning = FALSE}
# ====================================================
# Detach libraries and remove objects from environment
# ====================================================
Vectorize(detach)(name = paste0("package:", c("tidyverse", "mice", "gamm4",
                                              "mgcv", "modelr", "broom", "nlme", 
                                              "mediation", "MASS", "magrittr")), 
                  unload = TRUE, 
                  character.only = TRUE)

rm(list=ls())

```

